Le titre

### 2022-08-26 Manuscrit Thèse/chapter 4/Chapter 4.tex
tata

\section{Introduction to ensemble NV magnetometry}
Je vais en chier de ouf pour trouver des images.
\subsection{AC and DC magnetometry}
\subsection{Low field magnetometry}
Dans le dernier papier de Jelezko y'a des vrais raisons de faire du low field
\subsection{Microwave-free magnetometry}
Bubu et les russes
\subsubsection{Orientation-free magnetometry}
Arcizet

\section{Low field CR magnetometry}

>>>>

\section{Introduction to ensemble NV magnetometry}
Before we explore the application of low field depolarization to magnetometry, we must discuss the general field of NV magnetometry.

NV magnetometry is generally decomposed between single NV and ensemble magnetometry. Single NVs,often associated with scanning probes, offer a spatial resolution limited only by how far the magnetic source can be from the NV center (typically $\sim 10\ \rm nm$), but at the cost of a relatively low sensitivity (typically $\sim \mu \rm{T} / \sqrt{\rm Hz}$ \citep{pelliccione2016scanned}).

Ensemble NV centers center on the other hand offer sensitivities below $1\ \rm pT / \sqrt{\rm Hz}$ \citep{wolf2015subpicotesla}, at the cost of working working with samples of several hundreds of $\mu$m.

We will only focus here on NV ensemble magnetometry since we want to give elements of comparisons with our technique based on NV-NV CR. We will not try to give a complete overview of this field, but only to the elements close to the technique we present. For a general overview on microwave-based ensemble NV magnetometry, we recommend the excellent review from Barry et al \citep{barry2020sensitivity}.

\subsection{AC and DC magnetometry}
The most sensitive NV magnetometry protocols use the free precession of the spins to map a small change in the Zeeman energy into the phase of the spins, which is then converted in population. These protocols are generally distinguished between DC-broadband and AC-narrow band.

For DC-broadband magnetometry, the general technique consist of a Ramsey interferometry experiment, presented in chapter 1, which is limited by the spin inhomogeneous coherence time $T_2^*$. The bandwidth of the protocol is limited by the repetition rate of the experiment, generally up to $\sim 100\ \rm kHz$. Although less sensitive in theory, continuous-wave (CW) ODMR and pulsed ODMR are also often employed for DC magnetometry. The state of the art in term of DC ensemble magnetometry is a sensitivity of $\sim 20 pT/ \sqrt{\rm Hz}$
AC: pas oublier. J'ai oublié. Nan en vrai j'ai pas oublié, mais je le mettrai dans la partie sans uW
\subsection{Low field magnetometry}
Dans le dernier papier de Jelezko y'a des vrais raisons de faire du low field
\subsection{Microwave-free magnetometry}
Bubu et les russes 
\subsubsection{Orientation-free magnetometry}
Arcizet

\section{Low field depolarization magnetometry}
